Retrofitting Effect Handlers onto OCaml

### 2021-03-30 retro-concurrency.tex
use the right async citation later in the paper too

The results are presented in Table~\ref{tab:micro_noperform}. They show that
using effect handlers (concurrency monad) is 10.02$\times$ (67.09$\times$) more
expensive than the idiomatic implementation using non-tail calls. The
concurrency monad suffers due to the heap allocation of continuation frames
(which need to be garbage collected), whereas effect handlers benefit from
stack allocation of the frames. For example, the number of major collections
for the |ack| benchmark is 0 for stock OCaml, 1 for |MC| and 112 for |monad|.
Our concurrency monad (and other monadic concurrency libraries such as
Lwt~\cite{lwt} and Async~\cite{async}) also have other downsides -- exceptions,
backtraces, and DWARF unwinding are no longer useful due to the lack of a
stack.

>>>>

The results are presented in Table~\ref{tab:micro_noperform}. They show that
using effect handlers (concurrency monad) is 10.02$\times$ (67.09$\times$) more
expensive than the idiomatic implementation using non-tail calls. The
concurrency monad suffers due to the heap allocation of continuation frames
(which need to be garbage collected), whereas effect handlers benefit from
stack allocation of the frames. For example, the number of major collections
for the |ack| benchmark is 0 for stock OCaml, 1 for |MC| and 112 for |monad|.
Our concurrency monad (and other monadic concurrency libraries such as
Lwt~\cite{lwt} and Async~\cite[\S18]{rwo}) also have other downsides -- exceptions,
backtraces, and DWARF unwinding are no longer useful due to the lack of a
stack.
